Sound Automated Synthesis of Digital Controllers

### 2016-10-10 paper/paper.tex
Changes on section 2

A discrete-time linear system is said to be Bounded-Input and Bounded-Output (BIBO) stable if and only if every pole of its transfer function lies inside the unit circle. Analyzing the~\eqref{eq:outputfunctions} and based on assumption~\ref{assumption:cont_and_plant}, the following lemma states necessary conditions for stability of closed-loop system in figure~\ref{fig:sampledsystem}.

\begin{mylemma}{\cite{Bessa16,fadali}}
\label{internal_stab_lemma}
A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with transfer functions $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and $\hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is internally stable if and only if:
\begin{itemize}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{eq_int_stab}
S(z)=FWL[N_{C}(z)]\hat{N}_{G}(z)+FWL[D_{C}(z)]\hat{D}_{G}(z);
\end{equation}
\item the direct loop product $\frac{NFWL[_{C}(z)]}{FWL[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle;
\item the controller $\hat{C}(z)$ is a minimum-phase system. 
\end{itemize}
\end{mylemma}

>>>>

A discrete-time linear system is said to be Bounded-Input and Bounded-Output (BIBO) stable if and only if every pole of its transfer function lies inside the unit circle. Analyzing the~\eqref{eq:outputfunctions} and based on assumption~\ref{assumption:cont_and_plant}, the following lemma states necessary conditions for stability of closed-loop system in figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$ are bounded.

\begin{mylemma}{\cite{Bessa16,fadali}}
\label{internal_stab_lemma}
A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with transfer functions $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and $\hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is internally stable if and only if:
\begin{itemize}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{lemma:eq_int_stab}
S(z)=FWL[N_{C}(z)]\hat{N}_{G}(z)+FWL[D_{C}(z)]\hat{D}_{G}(z);
\end{equation}
\item the direct loop product $\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle;
\item the controller $\hat{C}(z)$ is a minimum-phase system. 
\end{itemize}
\end{mylemma}

The Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for synthesis of digital controllers able to stabilize closed loop system, considering plant parametric uncertainties ($\Delta G_{P}(z)$), quantization noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in digital controllers. Based on it, the model for plant uncertainty due quantization noise ($\Delta G(z)$ may be disregarded if the conditions on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantization noise is bounded.
